Wigglyhedra

### 2024-10-17 FPSAC25/wigglyhedraFPSAC.tex
improve FPSAC

We start by defining the wiggly complex, the clique complex of a compatibility relation on the following wiggly arcs.

@@

\begin{definition}
A \defn{wiggly pseudodissection}~$D$ is a set of pairwise compatible wiggly arcs which contains the exterior wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$. We denote by~$D^\circ \eqdef D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.

\begin{figure}[b]
\centerline{\includegraphics[scale=1.4]{wigglyPseudodissections}}
\caption{Three wiggly pseudodissections for~$n = 7$. The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue). The other two have $7$ pseudotriangles, and are obtained from each other by a flip.}
\label{fig:pseudodissections}
\end{figure}
\end{definition}

\begin{definition}
\label{def:wigglyComplex}
The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of subsets of pairwise compatible internal wiggly arcs.
%In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.

@@

\begin{proposition}
\label{prop:wigglyPseudotriangulations}
Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
Moreover, the following are equivalent:
\begin{compactenum}[(i)]
\item all wiggly cells of~$D$ are wiggly pseudotriangles,
\item $D$ contains~$n$ wiggly cells and is connected,
\item $D$ contains $2n-1$ internal wiggly arcs,
\item $D$ is an inclusion maximal wiggly pseudodissection.
\end{compactenum}
We then say that~$D$ is a \defn{wiggly pseudotriangulation}.
\end{proposition}

@@

\begin{proposition}
\label{prop:uerp}
Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
\begin{compactitem}
\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
\item $\beta \!\eqdef\! \big( i, j', {]i,j'[} \!\ssm\! (B \!\cup\! B'), {]i,j'[} \!\cap\! (B \!\cup\! B') \big)$ and~$\beta' \!\eqdef\! \big( i', j, {]i',j[} \!\cap\! (A \!\cup\! A'), {]i',j[} \!\ssm\! (A \!\cup\! A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ with~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
(In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
\end{compactitem}
%See \cref{fig:incompatible3} for illustrations.
%(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
%
%\begin{figure}

%\vspace{-.1cm}
\centerline{\includegraphics[scale=1.3]{incompatible3}}
%\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
%\label{fig:incompatible3}
%\end{figure}
\vspace{-.4cm}
\end{proposition}

@@

\begin{definition}
\label{def:wigglyPermutation}
A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns:
\begin{compactitem}
\item $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$,
\item $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$.
\end{compactitem}
\end{definition}

\begin{example}
\label{exm:allSmallWigglyPermutations}
For~$n = 1$, the $2$ wiggly permutations of~$[2]$ are~$12$ and~$21$.
For~$n = 2$, the $14$ wiggly permutations of~$[4]$ are
\vspace{-.1cm}
\[
1234, 1243, 1342, 1423, 1432, 2134, 2143, 3412, 3421, 4123, 4132, 4213, 4312, 4321.
\]
%The wiggly permutations of~$[6]$ are
%\begin{gather*}
%123456, 213456, 134256, 124356, 123564, 123465, 342156, 214356, 213564, 213465, 341256, 143256, \\
%134562, 134265, 142356, 125643, 124365, 135642, 125634, 123654, 123645, 432156, 345621, 342165, \\
%421356, 215643, 214365, 356421, 215634, 213654, 213645, 431256, 341562, 341265, 413256, 143562, \\
%143265, 134652, 134625, 412356, 156423, 142365, 156243, 126543, 126435, 356412, 156342, 136542, \\
%156234, 126534, 126354, 136425, 126345, 435621, 432165, 346521, 346215, 564213, 421365, 562143, \\
%216543, 216435, 563421, 365421, 562134, 216534, 216354, 364215, 216345, 431562, 431265, 345612, \\
%341652, 341625, 413562, 413265, 156432, 143652, 143625, 136452, 564123, 412365, 561423, 165423, \\
%164235, 561243, 165243, 162543, 162435, 563412, 365412, 561342, 165342, 163542, 561234, 165234, \\
%162534, 162354, 364125, 163425, 162345, 564321, 436521, 436215, 364521, 654213, 642135, 652143, \\
%621543, 621435, 653421, 635421, 652134, 621534, 621354, 634215, 621345, 435612, 431652, 431625, \\
%346512, 346152, 346125, 564132, 413652, 413625, 561432, 165432, 164352, 164325, 364152, 163452, \\
%654123, 641235, 651423, 615423, 614235, 651243, 615243, 612543, 612435, 653412, 564312, 635412, \\
%651342, 615342, 613542, 651234, 615234, 612534, 612354, 634125, 613425, 612345, 654321, 643521, \\
%643215, 634521, 436512, 436152, 436125, 364512, 654132, 641352, 641325, 651432, 615432, 614352, \\
%614325, 634152, 613452, 654312, 643125, 643512, 643152, 634512.
%\end{gather*}
\end{example}

@@

\parpic(3.6cm,5cm)(-10pt, 133pt)[r][b]{\includegraphics[scale=2]{bijection}}{
\begin{definition}
\label{def:bijection1}
Consider a wiggly pseudotriangulation~$T$.
Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
Define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
See example on the right.
\end{definition}

\begin{definition}
\label{def:bijection2}
For a wiggly permutation~$\sigma$ of~$[2n]$, define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
\begin{alignat*}{3}
i & \eqdef \max \{0\} \cup \set{i \!\in\! [n]}{2i-1 \!\in\! \sigma([k]) \!\!\not\ni\! 2i}\!, \quad &
A & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])}\!, \\
j & \eqdef \min \{n+1\} \cup \set{j \!\in\! [n]}{2j \!\in\! \sigma([k]) \!\!\not\ni\! 2j-1}\!, \;\, &
B & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing} \!.
\end{alignat*}
\end{definition}
}

@@

\begin{definition}
\label{def:gvectors}
The \defn{$\b{g}$-vector}~$\b{g}(\alpha)$ of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
\vspace{-.25cm}
\begin{align*}
\alpha^+ & \eqdef \big(\{2i-1, 2j\} \ssm \{-1, 2n+2\} \big) \cup \set{2a-1}{a \in A} \cup \set{2a}{a \in A},
\\
\alpha^- & \eqdef \big(\{2i, 2j-1\} \ssm \{0, 2n+1\} \big) \cup \set{2b-1}{b \in B} \cup \set{2b}{b \in B}.
\\[-.9cm]
\end{align*}
%If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\b{g}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
%Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
\noindent
We define~$\b{g}(D) \eqdef \set{\b{g}(\alpha)}{\alpha \in D^\circ}$ for a set~$D$ of wiggly arcs.
\end{definition}

@@

\begin{definition}
\label{def:cvectors}
The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a \mbox{wiggly pseudotriangulation~$T$} is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)\!}{\!\b{g}(\alpha)} \!=\! 1$ and~$\dotprod{\b{c}(\alpha, T)\!}{\!\b{g}(\alpha')} \!=\! 0$~for~all wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
That is, $\b{c}(T) \eqdef \! \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ and~$\b{g}(T)$ are dual bases~in~$\HH_{2n}$.
\end{definition}

@@

Combining \cref{prop:linearDependences,prop:wallCrossingInequalities}, the incompatibility number satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$, from which we derive our main statement.
%that it behaves properly with respect to the linear dependences of

@@

In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 = \delta_{n+1} = 0$.
We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice % of \cref{sec:wigglyPermutations} 
and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron. % of \cref{sec:wigglyhedron}.
\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.

@@

\begin{proposition}
\label{prop:CambrianLattice}
The $\delta$-triangulation, $\delta$-permutation, \mbox{$\delta$-wiggly} pseudotriangulation, and $\delta$-wiggly permutation lattices are all isomorphic, and are known as the \defn{$\delta$-Cambrian~lattice}~\cite{Reading-CambrianLattices}.
\end{proposition}

@@

\cref{conj:polytopality} holds in two extreme situations: the wiggly complex~$\wigglyComplex_P$ is realized
\begin{compactitem}
\item by the wigglyhedron of~\cref{thm:wigglyhedron} when the point set~$P$ is alogned, and
\item by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}, realizing the flip graph on the original pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, when the point set~$P$ is in general position.
\end{compactitem}

>>>>

We start by defining the wiggly complex, the clique complex of a compatibility relation on the following wiggly arcs.
See \cref{fig:pseudodissections}.

@@

\begin{definition}
A \defn{wiggly pseudodissection}~$D$ is a set of pairwise compatible wiggly arcs which contains the exterior wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$. We denote by~$D^\circ \!\eqdef\! D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.

\begin{figure}[b]
\centerline{\includegraphics[scale=1.4]{wigglyPseudodissections}}
\caption{Three wiggly pseudodissections for~$n = 7$. The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue). The other two have $7$ wiggly pseudotriangles, and are obtained from each other by a flip.}
\label{fig:pseudodissections}
\end{figure}
\end{definition}

\begin{definition}
\label{def:wigglyComplex}
The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of subsets of pairwise compatible internal wiggly arcs.
%In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.
See \cref{fig:wigglyComplex}\,(left).

@@

\begin{proposition}
\label{prop:wigglyPseudotriangulations}
Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
Moreover, the following assertions are equivalent:
\begin{compactenum}[(i)]
\item all wiggly cells of~$D$ are wiggly pseudotriangles,
\item $D$ contains~$n$ wiggly cells and is connected,
\item $D$ contains $2n-1$ internal wiggly arcs,
\item $D$ is an inclusion maximal wiggly pseudodissection.
\end{compactenum}
We then say that~$D$ is a \defn{wiggly pseudotriangulation}.
\end{proposition}

@@

\begin{proposition}
\label{prop:uerp}
Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
\begin{compactitem}
\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
\item $\beta \!\eqdef\! \big( i', j, {]i,j'[} \!\ssm\! (B \!\cup\! B'), {]i,j'[} \!\cap\! (B \!\cup\! B') \big)$ and~$\beta' \!\eqdef\! \big( i, j', {]i',j[} \!\cap\! (A \!\cup\! A'), {]i',j[} \!\ssm\! (A \!\cup\! A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and $\alpha$ crosses~$\alpha'$ from north-west to south-east.
(In other words, $\beta$ is the wiggly arc starting at~$i'$ and ending at~$j$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i$ and ending~at~$j'$ which follows the upper hull of~$\alpha$~and~$\alpha'$.)
\end{compactitem}
%See \cref{fig:incompatible3} for illustrations.
%(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
%
%\begin{figure}

\vspace{.1cm}
\centerline{\includegraphics[scale=1.55]{incompatible3}}
%\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
%\label{fig:incompatible3}
%\end{figure}
\end{proposition}

@@

\begin{definition}
\label{def:wigglyPermutation}
A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns
\begin{compactitem}
\item $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$,
\item $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$.
\end{compactitem}
\end{definition}

\begin{example}
\label{exm:allSmallWigglyPermutations}
For~$n = 1$, the $2$ wiggly permutations of~$[2]$ are~$12$ and~$21$.
For~$n = 2$, the $14$ wiggly permutations of~$[4]$ are
\[
1234, \; 1243, \; 1342, \; 1423, \; 1432, \; 2134, \; 2143, \; 3412, \; 3421, \; 4123, \; 4132, \; 4213, \; 4312, \; 4321.
\]
%The wiggly permutations of~$[6]$ are
%\begin{gather*}
%123456, 213456, 134256, 124356, 123564, 123465, 342156, 214356, 213564, 213465, 341256, 143256, \\
%134562, 134265, 142356, 125643, 124365, 135642, 125634, 123654, 123645, 432156, 345621, 342165, \\
%421356, 215643, 214365, 356421, 215634, 213654, 213645, 431256, 341562, 341265, 413256, 143562, \\
%143265, 134652, 134625, 412356, 156423, 142365, 156243, 126543, 126435, 356412, 156342, 136542, \\
%156234, 126534, 126354, 136425, 126345, 435621, 432165, 346521, 346215, 564213, 421365, 562143, \\
%216543, 216435, 563421, 365421, 562134, 216534, 216354, 364215, 216345, 431562, 431265, 345612, \\
%341652, 341625, 413562, 413265, 156432, 143652, 143625, 136452, 564123, 412365, 561423, 165423, \\
%164235, 561243, 165243, 162543, 162435, 563412, 365412, 561342, 165342, 163542, 561234, 165234, \\
%162534, 162354, 364125, 163425, 162345, 564321, 436521, 436215, 364521, 654213, 642135, 652143, \\
%621543, 621435, 653421, 635421, 652134, 621534, 621354, 634215, 621345, 435612, 431652, 431625, \\
%346512, 346152, 346125, 564132, 413652, 413625, 561432, 165432, 164352, 164325, 364152, 163452, \\
%654123, 641235, 651423, 615423, 614235, 651243, 615243, 612543, 612435, 653412, 564312, 635412, \\
%651342, 615342, 613542, 651234, 615234, 612534, 612354, 634125, 613425, 612345, 654321, 643521, \\
%643215, 634521, 436512, 436152, 436125, 364512, 654132, 641352, 641325, 651432, 615432, 614352, \\
%614325, 634152, 613452, 654312, 643125, 643512, 643152, 634512.
%\end{gather*}
\end{example}

@@

\parpic(3.6cm,3.5cm)(-10pt, 133pt)[r][b]{\includegraphics[scale=2]{bijection}}{
\begin{definition}
\label{def:bijection1}
Consider a wiggly pseudotriangulation~$T$.
Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
Define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
See example on the right.
\end{definition}

\begin{definition}
\label{def:bijection2}
For a wiggly permutation~$\sigma$ of~$[2n]$, define~$\Psi(\sigma) \eqdef\! \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
\begin{alignat*}{3}
i & \eqdef \max \{0\} \cup \set{i \!\in\! [n]}{2i-1 \!\in\! \sigma([k]) \!\!\not\ni\! 2i}\!, \quad &
A & \eqdef \set{\ell \!\in\! {]i,j[}}{\!\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])}\!, \\
j & \eqdef \min \{n+1\} \cup \set{j \!\in\! [n]}{2j \!\in\! \sigma([k]) \!\!\not\ni\! 2j-1}\!, \;\, &
B & \eqdef \set{\ell \!\in\! {]i,j[}}{\!\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing} \!.
\end{alignat*}
\end{definition}
}

@@

\begin{definition}
\label{def:gvectors}
The \defn{$\b{g}$-vector}~$\b{g}(\alpha)$ of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
\begin{align*}
\alpha^+ & \eqdef \big(\{2i-1, 2j\} \ssm \{-1, 2n+2\} \big) \cup \set{2a-1}{a \in A} \cup \set{2a}{a \in A},
\\
\alpha^- & \eqdef \big(\{2i, 2j-1\} \ssm \{0, 2n+1\} \big) \cup \set{2b-1}{b \in B} \cup \set{2b}{b \in B}.
\end{align*}
%If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\b{g}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
%Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
\noindent
We define~$\b{g}(D) \eqdef \set{\b{g}(\alpha)}{\alpha \in D^\circ}$ for a set~$D$ of wiggly arcs.
\end{definition}

@@

\begin{definition}
\label{def:cvectors}
The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a \mbox{wiggly pseudotriangulation~$T$} is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)\!}{\!\b{g}(\alpha)} \!=\! 1$ and~$\dotprod{\b{c}(\alpha, T)\!}{\!\b{g}(\alpha')} \!=\! 0$~for~all wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
That is, $\b{c}(T) \eqdef \! \set{\b{c}(\alpha, T)}{\alpha \!\in\! T^\circ}$ and~$\b{g}(T)$ are dual bases~in~$\HH_{2n}$.
\end{definition}

@@

Combining \cref{prop:linearDependences,prop:wallCrossingInequalities}, the incompatibility numbers satisfy all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$, from which we derive our main statement.
%that it behaves properly with respect to the linear dependences of

@@

In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 \eqdef \delta_{n+1} \eqdef 0$.
We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice % of \cref{sec:wigglyPermutations} 
and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron. % of \cref{sec:wigglyhedron}.
\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.

@@

\begin{proposition}
\label{prop:CambrianLattice}
The $\delta$-triangulation, $\delta$-permutation, \mbox{$\delta$-wiggly} pseudotriangulation, and $\delta$-wig\-gly permutation lattices are all isomorphic, and are known as the \defn{$\delta$-Cambrian~lattice}~\cite{Reading-CambrianLattices}.
\end{proposition}

@@

\cref{conj:polytopality} holds in two extreme situations: the wiggly complex~$\wigglyComplex_P$ is realized
\begin{compactitem}
\item by the wigglyhedron of~\cref{thm:wigglyhedron} when the point set~$P$ is aligned, and
\item by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}, realizing the flip graph on the original pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, when the point set~$P$ is in general position.
\end{compactitem}
